### 2019-08-22 manuscript/methods.tex
references Rosana to be merged with boris and partial figure editing

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states.pdf}
\caption{
Character states used in the models.
(A) Each species retained on the phylogeny belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known. 
Number of species in each category is indicated; for example, 70 species are self-compatible with unknown ploidy.
Character state abbreviations are: $I$ for self-incompatible, $C$ for self-compatible, $D$ for diploid, $P$ for polyploid, $?$ for unknown.
Because polyploidization breaks this form of self-incompatibility, self-incompatible species with unobserved ploidy ($I?$) are taken to be diploid ($ID$), and polyploid species with unobserved breeding system ($?P$) are taken to be SC ($CP$).
(B) Category groupings into states for each model class.
In the ploidy-only models (M1- M10), states are coded as $D$ \& $P$ when uncertain/consistent with either state; in the breeding system-only models (M11-M15) such states are coded as $C$; in the ploidy and breeding system models (M16-M29), they are coded as $CD$ \& $CP$.
In the hidden-trait models, all species could take on either of two `hidden' character states. %IM: #33 
Two species, \emph{Lycium californicum} and \emph{Solanum bulbocastanum}, are simultaneously $ID$ and $CP$, and by adding them the sample adds to the total of 651 taxa used for analyses.
}
\label{figure:stateclassifications}
\end{figure}

@@

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M2    & M3     & M4    & M5     & Evidence                                                                                     \\ \hline
M1. D/P              & -1283.76                                                          & 59.90 & 49.23  & 60.48 & 58.82  & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M1\end{tabular}            \\ \hline
\textbf{M2. CID D/P} & \textbf{-1223.86}                                                 &       & -10.66 & 0.579 & -1.079 & \begin{tabular}[c]{@{}l@{}}Strong preference for \\ M2 over M1\end{tabular}              \\ \hline
M3. D/P+A/B          & -1234.52                                                          &       &        & 11.24 & 9.58   & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M4. D/P+A/B asym}     & \textbf{-1223.28}                                                          &       &        &       & -1.658 & \begin{tabular}[c]{@{}l@{}}Moderate evidence for\\ only asymmetric hidden rates\end{tabular} \\\hline
M5. D/P+A/B all asym & -1224.93                                                          &       &        &       &        &          \\ \hline                                                                                   
\end{tabular}
\caption{Bayes factors of  ploidy-only models without diplodization. Numbers greater that 1 mean moderate support relative to the model in the row label.  Conventional threshold for `strong' support is 10. The best models are written in bold. }
\label{table:bayesfactors}
\end{table}

% B: M111->M11
\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                      & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M12   & M13   & M14   & M15   & Evidence                                                                                       \\ \hline
M11. I/C                   & -1309.07                                                          & 41.13 & 38.59 & 61.34 & 61.40 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M11\end{tabular}            \\ \hline
M12. CID I/C               & -1267.93                                                          &       & -2.53 & 20.21 & 20.37 & \begin{tabular}[c]{@{}l@{}}Models with asymmetric rates\\ are preferred over  M12\end{tabular} \\ \hline
M13. I/C+A/B               & -1270.47                                                          &       &       & 22.75 & 22.80 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M14. I/C+A/B asym} & \textbf{-1247.72}                                                 &       &       &       & 0.05 & No evidence                                                                                    \\ \hline
\textbf{M15. I/C+A/B all asym }     & \textbf{ -1247.66}                                                          &       &       &       &       &       \\ \hline                                                                                        
\end{tabular}
\caption{Bayes factors of breeding system-only models. Results indicate that the HiSSE models with asymmetric rates (M14, M15) are strongly preferred over every other model.}
\label{table:M11M15}
\end{table}

@@

\begin{table}[]
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|c|c|c|c|}
\hline
Model                       & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & Comparison  & K=ln(BF($M_{i}$,$M_{ii}$)) & \begin{tabular}[c]{@{}l@{}}Preferred\\ Model (Evidence)\end{tabular} \\ \hline
M26. Lumped D/P             & -1463.22                                                          & M26 vs. M16 & 4.10            & M16 (Moderate)                                                       \\
\textbf{M16. ID/CD/CP}      & \textbf{-1459.11}                                                 &             &                 &                                                                      \\ \hline
M27. Lumped D/P+A/B         & -1417.67                                                          & M27 vs. M23 & 3.678           & M23 (Moderate)                                                       \\
\textbf{M23. ID/CD/CP +A/B} & \textbf{-1414.00}                                                 &             &                 &                                                                      \\ \hline
M28. Lumped I/C             & -1458.41                                                          & M28 vs. M16 & -0.69           & No evidence                                                          \\
\textbf{M16. ID/CD/CP}      & \textbf{-1459.11}                                                 &             &                 &                                                                      \\ \hline
M29. Lumped I/C+ A/B        & -1416.60                                                          & M29 vs. M23 & 2.60            & M23 (Moderate)                                                       \\
\textbf{M23. IC/CD/CP+A/B}  & \textbf{-1414.00}                                                 &             &                 &                                                                      \\ \hline
\end{tabular}
\caption{Test for adding a focal trait to a binary state model via Bayes factors. Three-state models are moderately preferred over two-state models. The evidence is stronger towards the inclusion of breeding systems in ploidy models (M26, M27) than the inclusion of ploidy in breeding system models (M29, M29)}
\label{table:lumped}
\end{table}

\begin{figure}
\includegraphics[width=\textwidth]{alldiversificationasymhidden.pdf} 
\caption{Net diversification rates for SSE models of focal traits with or without hidden state. 
Each panel contains a graphical summary of estimated model parameters and displays posterior distributions for net diversification estimates.}
\label{figure:netdivall}
\end{figure}

>>>>

@@

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M2    & M3     & M4    & M5     & Evidence                                                                                     \\ \hline
M1. D/P              & -1283.76                                                          & 59.90 & 49.23  & 60.48 & 58.82  & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M1\end{tabular}            \\ \hline
\textbf{M2. CID D/P} & \textbf{-1223.86}                                                 &       & -10.66 & 0.579 & -1.079 & \begin{tabular}[c]{@{}l@{}}Strong preference for \\ M2 over M1\end{tabular}              \\ \hline
M3. D/P+A/B          & -1234.52                                                          &       &        & 11.24 & 9.58   & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M4. D/P+A/B asym}     & \textbf{-1223.28}                                                          &       &        &       & -1.658 & \begin{tabular}[c]{@{}l@{}}Moderate evidence for\\ only asymmetric hidden rates\end{tabular} \\\hline
M5. D/P+A/B all asym & -1224.93                                                          &       &        &       &        &          \\ \hline                                                                                   
\end{tabular}
\caption{Bayes factors for ploidy only models without diplodization.  Numbers greater that 1 mean moderate support relative to the model in the row label.  Conventional threshold for `strong' support is 10.  The preferred models are M2 and M4 (bold). }
\label{table:bayesfactors}
\end{table}

% B: M111->M11
\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                      & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M12   & M13   & M14   & M15   & Evidence                                                                                       \\ \hline
M11. I/C                   & -1309.07                                                          & 41.13 & 38.59 & 61.34 & 61.40 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M11\end{tabular}            \\ \hline
M12. CID I/C               & -1267.93                                                          &       & -2.53 & 20.21 & 20.37 & \begin{tabular}[c]{@{}l@{}}Models with asymmetric rates\\ are preferred over  M12\end{tabular} \\ \hline
M13. I/C+A/B               & -1270.47                                                          &       &       & 22.75 & 22.80 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M14. I/C+A/B asym} & \textbf{-1247.72}                                                 &       &       &       & 0.05 & No evidence                                                                                    \\ \hline
\textbf{M15. I/C+A/B all asym }     & \textbf{ -1247.66}                                                          &       &       &       &       &       \\ \hline                                                                                        
\end{tabular}
\caption{Bayes factors for breeding system only models. Results indicate that the HiSSE models (bold) with asymmetric rates (M14, M15) are strongly preferred over every other model.}
\label{table:M11M15}
\end{table}

@@

\begin{table}[]
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|c|c|c|c|}
\hline
Model                       & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & Comparison  & K=ln(BF($M_{i}$,$M_{ii}$)) & \begin{tabular}[c]{@{}l@{}}Preferred\\ Model (Evidence)\end{tabular} \\ \hline
M26. Lumped D/P             & -1463.22                                                          & M26 vs. M16 & 4.10            & M16 (Moderate)                                                       \\
\textbf{M16. ID/CD/CP}      & \textbf{-1459.11}                                                 &             &                 &                                                                      \\ \hline
M27. Lumped D/P+A/B         & -1417.67                                                          & M27 vs. M23 & 3.678           & M23 (Moderate)                                                       \\
\textbf{M23. ID/CD/CP +A/B} & \textbf{-1414.00}                                                 &             &                 &                                                                      \\ \hline
M28. Lumped I/C             & -1458.41                                                          & M28 vs. M16 & -0.69           & No evidence                                                          \\
M16. ID/CD/CP      & \textbf{-1459.11}                                                 &             &                 &                                                                      \\ \hline
M29. Lumped I/C+ A/B        & -1416.60                                                          & M29 vs. M23 & 2.60            & M23 (Moderate)                                                       \\
\textbf{M23. IC/CD/CP+A/B}  & \textbf{-1414.00}                                                 &             &                 &                                                                      \\ \hline
\end{tabular}
\caption{Testing the addition of a focal trait to a binary state model via Bayes factors. Three-state models are moderately preferred over two-state models. There is moderate evidence towards the inclusion of breeding systems in ploidy models (M16, M23, bold). There is moderate or no evidence towards the  inclusion of ploidy in breeding system models (M23, bold).}
\label{table:lumped}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states.pdf}
\caption{
Character states used in the models.
(A) Each species retained on the phylogeny belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known. 
Number of species in each category is indicated; for example, 70 species are self-compatible with unknown ploidy.
Character state abbreviations are: $I$ for self-incompatible, $C$ for self-compatible, $D$ for diploid, $P$ for polyploid, $?$ for unknown.
Because polyploidization breaks this form of self-incompatibility, self-incompatible species with unobserved ploidy ($I?$) are taken to be diploid ($ID$), and polyploid species with unobserved breeding system ($?P$) are taken to be SC ($CP$).
(B) Category groupings into states for each model class.
In the ploidy-only models (M1- M10), states are coded as $D$ \& $P$ when uncertain/consistent with either state; in the breeding system-only models (M11-M15) such states are coded as $C$; in the ploidy and breeding system models (M16-M29), they are coded as $CD$ \& $CP$.
In the hidden-trait models, all species could take on either of two `hidden' character states. %IM: #33 
Two species, \emph{Lycium californicum} and \emph{Solanum bulbocastanum}, are simultaneously $ID$ and $CP$, and by adding them the sample adds to the total of 651 taxa used for analyses.
}\label{figure:stateclassifications}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{alldiversificationasymhidden.pdf} 
\caption{Net diversification rates for SSE models of focal traits with or without hidden state. 
(A) Ploidy only model (M1) showing higher net diversification linked to diploid state $D$ compared to polyploid state $P$.
(B) Ploidy only model with hidden states  model (M4) showing that the net diversification is higher for hidden state $B$ compared to hidden state $A$ and both diploid and polyploid states within each hidden traits have overlapping net diversification rates.
(C) Breeding system model only (M9) showing higher net diversification linked to self-incompatible $I$ state compared to self-compatible state $C$.
(D) Breeding system with hidden states model (M11) showing differences in both hidden states in net diversification and little to no overlapping in between self-compatible \vs self-compatible states.
(E) Ploidy and breeding system model (M13) showing higher net diversification linked to self-incompatible diploid state $ID$ compared to both self-compatible states despite ploidy level ($CD, CP$).
(F) Ploidy, breeding system, and hidden states modl (M16) showing a similar pattern that panel (E) within each hidden state $A$ and $B$. For hidden state $B$ there is a larger overlap of net diversification between states $CD_B$ and $ID_B$.}
\label{figure:netdivall}
\end{figure}
